### 2024-06-18 Thesis.tex
fix underfull hboxes

\bibitem{Weston} Weston T., An~introduction to~cobordism theory~/ T.~Weston~//
Stanford University : [сайт].~— URL: \url{https://math.stanford.edu/~ralph/morsecourse/cobordismintro%20.pdf} (дата обращения: 23.08.2022).

>>>>

\bibitem{Weston} Weston T., An~introduction to~cobordism theory~/ T.~Weston~//
{Stan\-ford} University. School of~Humanities and~Sciences.
The~Department of~{Math\-e\-mat\-ics} : [сайт].~— URL: \url{https://math.stanford.edu/~ralph/morsecourse/cobordismintro%20.pdf} (дата обращения: 23.08.2022).
